---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# defmacroex

<!-- badges: start -->
<!-- badges: end -->

Just an example of how to use the `defmacro` package.

## Example

The package exports a function called `analyze_dataset` with the following code that defines its own pipe function and a zero overhead logging macro.

```{r, eval=FALSE}
analyze_dataset <- function(data) {
  log("Entering pipe")
  result <- pipe({
    data
    dplyr::filter(hp > constexpr(50 + 50 + qnorm(0.975)))
    dplyr::group_by(cyl)
    dplyr::summarise(dplyr::n())
  })
  log("Returning result")
  result
}
```

During package load, the code gets replaced by the expanded version of the macro. This means the function does not have any runtime overhead.

```{r}
defmacroex::analyze_dataset
```

Had we enabled logging through an environment variable, the logging code would have been added to the function:

```{r}
unloadNamespace("defmacroex")
withr::with_envvar(c("LOGGING" = "1"), {
  defmacroex::analyze_dataset
})
```

